---
title: "DDS Case Study 1"
author: "Ganesh  and Jeff Leath"
date: "October 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## Beginning

This is a placehold.  I am building a shell we can use to build the workproduct.

```{r}
1+1
```

## Introduction

Placeholder for introduction to the project.

a.	Introduction to the project. The introduction should not reference a project, persay. No part of this should be informal.


## Questions


1.	How many breweries are present in each state?

```{r}
1+1
```


2.	Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

```{r}
1+1
```
3.	Report the number of NA's in each column.

```{r}
1+1
```
4.	Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

```{r}
1+1
```

5.	Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

```{r}
1+1
```

6.	Summary statistics for the ABV variable.

```{r}
1+1
```

7.	Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

```{r}
2+2
```


## Conclussion

Placeholder for conclussion to the project.

